Scientific Reasoning with LLMs

### 2024-10-29 docs/proposal/main.tex
kept only multimodal FMs in preliminary list

\paragraph{RQ1} 
We plan to start by prompting a multimodal model with reasoning capabilities with a zero-shot and few-shot prompting settings. Preliminary list of foundation models to be compared as baselines is: CLIP, GPT4o, T5, BigGAN, Gemini; small models: TinyCLIP, T5-Small; Llama models. This simple generation will be compared with an agent-based approach using the same models, which will now include augmented retrieval of information on the scientific task from domain-specific texts.

@@

\paragraph{RQ3}
In order to distill the knowledge from the system obtained at previous steps, we plan to do the model distillation with Chain-of-Thought Prompting for Reasoning approach. Following techniques described in \cite{magister2022teaching} \cite{wei2022chain}, the student model will be fine-tuned using these CoT responses together with any additional information the agent has retrieved from external sources to produce intermediate reasoning steps. At the same time, the teacher model generates multiple CoT responses, and the student learns from the aggregate (self-consistent) reasoning paths. 
The foundation model to serve as student LLM should be small, multimodal, capable of reasoning and capable of acquiring new distilled knowledge. A preliminary list of candidate models: small Llama models, MiniGPT-4, small FLAVA models distilUNITER, lxmert, distilled ViLT, to be also compared with text-only DeBERTa-V3 Small / Base, DistilBERT, GPT-2 Medium.
%The described approach can help the student model avoid common mistakes and output more consistent answers.

>>>>

\paragraph{RQ1} 
We plan to start by prompting a multimodal model with reasoning capabilities with a zero-shot and few-shot prompting settings. Preliminary list of foundation models to be compared as baselines is: CLIP, GPT4o (GPT4-V), T5, BigGAN, Gemini; small models: TinyCLIP, T5-Small; Llama models. This simple generation will be compared with an agent-based approach using the same models, which will now include augmented retrieval of information on the scientific task from domain-specific texts.

@@

\paragraph{RQ3}
In order to distill the knowledge from the system obtained at previous steps, we plan to do the model distillation with Chain-of-Thought Prompting for Reasoning approach. Following techniques described in \cite{magister2022teaching} \cite{wei2022chain}, the student model will be fine-tuned using these CoT responses together with any additional information the agent has retrieved from external sources to produce intermediate reasoning steps. At the same time, the teacher model generates multiple CoT responses, and the student learns from the aggregate (self-consistent) reasoning paths. 
The foundation model to serve as student LLM should be small, multimodal, capable of reasoning and capable of acquiring new distilled knowledge. A preliminary list of candidate models: small Llama and LLaVA models, MiniGPT-4, small FLAVA models, distilUNITER, lxmert, distilled ViLT.
%The described approach can help the student model avoid common mistakes and output more consistent answers.
